\documentclass[12pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
CIEE, Attn: Study\\
300 Fore St\\
Portland, ME 04101}

% opening here
\opening{}
\raggedright % if you like this
\setlength{\parindent}{15pt} % if you like this

This letter is in support of MIDN 3/C Nicholas Forys' application to the CIEE program to study abroad in Seoul, South Korea.  I have known Mr. Forys for one year as his instructor in EW281C/EW282C Introduction to Drone Technology (our ``School of Drones'' course sequence). I am very happy to recommend Mr. Forys for your program and believe he will do well. 

Mr. Forys is a student in my department majoring in Robotics and Control Engineering.  He has done well achieving a 3.9 GPA in difficult engineering coursework (statics, dynamics, differential equations, programming, design, and mechatronics) in addition to my classes. As testament to his technical skills and engineering abilities, Forys was selected for an internship at Lawrence Livermore this summer working on carbon fixation techniques for carbon sequestration, as climate change mitigation.

While I have not taught Mr. Forys in a humanities class, I understand he is a member of the Korean-American Midshipmen Association, and is currently attending weekend Korean language lessons. In addition, he is planning a Spring break trip to Spain with three other midshipmen. Forys has also been a moderator for our Naval Academy Science and Engineering Conference, leading group discussions on environmental with civilians, military, and international participants. These show he has the skills and judgment to participate, and bring fresh perspectives to, an international program like yours. 


\closing{~} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}


